Solutions to the potential for unintended conservation consequences of MPAs

### 2021-07-12 documents/03_marlin_paper.Rmd
passing to squid
checked that revamped version works

# Introduction

>>>>

** something to piont out: increased catches are a paradox, either come from rebuilding stock or concentrated fishing, but trajectory can tell you something. not possible for MPAs to increase catches without decreasing catches first if they are rebuilding? **
# Introduction

Empirically, how do you differentiate increase in catch from fishing harder vs increases in catch from rebuilding: rebuilding has to have a decrease at first
